On The Benefits of Magnitude Estimation Relevance Assessments for Information Retrieval Evaluation

### 2016-09-13 6_results_RQ2.tex
Minor changes

We now turn to the second research question and 
investigate whether crowdsourcing is a valid methodology to gather magnitude
estimation scores. 
We have already touched upon several related issues: the quality
checks that we put in place in our experiment and that allowed us to
gather good quality data (Section~\ref{sec:quality-checks}); the
approximately log-normal distribution of our magnitude estimation
scores (Section~\ref{sec:score-distribution}); the normalization and
aggregation functions (Section~\ref{sec:score-normalization}); and the
overall agreement of the magnitude estimation scores with official
relevance judgments (Section~\ref{sec-rq1}). 
We now present more details, focusing on measuring judge
agreement, on analyzing disagreement with official judges, and on
discussing what happens when the number of collected judgments 
decreases.

>>>>

We now turn to the second research question RQ\ref{item:rq4} and 
investigate whether crowdsourcing is a valid methodology to gather magnitude
estimation scores. 
We have already touched upon several related issues: the quality
checks that we put in place in our experiment and that allowed us to
gather good quality data (Section~\ref{sec:quality-checks}); the
approximately log-normal distribution of our magnitude estimation
scores (Section~\ref{sec:score-distribution}); the normalization and
aggregation functions (Section~\ref{sec:score-normalization}); and the
overall agreement of the magnitude estimation scores with official
relevance judgments (Section~\ref{sec-rq1}). 
We now present more details, focusing on measuring judge
agreement, on analyzing disagreement with official judges, and on
discussing what happens when the number of collected judgments 
decreases.
